---
title: "Best books of 20th Century" 
author: "- M.Sun - Feb. 11, 2018"
# date: "Fubruary 11, 2018"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
#   social: menu
#   source_code: embed
runtime: shiny
---

```{r global}
# load packages
# devtools::install_github('rstudio/rmarkdown')
library(flexdashboard)
library(shinyWidgets)
library(dplyr)
library(DT)
library(ggplot2)
library(magrittr)
library(stringr)

book_list = read.csv('~/NYC_data_science/projects/project2/book_list/book_list.csv', 
                     stringsAsFactors = F)
book_list = book_list %>% select(ranking, year, title, author, pages, 
                                      avg_rating, description, awards) %>%
    filter(year>=1900 & year <2001) 

# global function definition
search_book <- function(pattern_str){
    function(source_str){
        str_detect(source_str, pattern = pattern_str)    
    }
}

# global book search function
# s_pattern: string pattern to be searched
# column_name: list of string sources under column name
# return: a list of books matching the search pattern,
#         ordered by the year and alphabetical order of title
return_books <- function(s_pattern, column_name){
    search_str = search_book(tolower(s_pattern))
    book_column = book_list %>% select(tolower(column_name))
    book_column = sapply(book_column, tolower)
    book_matched = sapply(book_column, search_str)
    book_list_final = book_list %>% filter(book_matched) %>% arrange(year, title)
    return(book_list_final)
}

```

Sidebar {.sidebar}
=====================================
```{r global_sidebar}
radioButtons(inputId = 'decade_choice', 
             label = h3('Select Decade'), 
             choices = list(1900, 1910, 1920, 1930, 1940, 1950, 
                            1960, 1970, 1980, 1990),
             selected = 1990)

searchInput(inputId = 'search_item',
            label = 'Enter your search:',
            placeholder = 'This is a placeholder',
            btnSearch = icon('search'),
            btnReset = icon('remove'),
            width = '100%'
)

radioButtons(inputId = 'search_by', 
             label = h3('Search Category'), 
             choices = list('author', 'title', 'awards'),
             selected = 'author')

checkboxGroupInput(inputId = 'order_by', 
             label = h3('Order book list by:'), 
             choices = list('ranking', 'year', 'title', 'author','avg_rating'),
             selected = 'ranking')
```

Trend
=====================================  

### Great books with great stories always intrigue me. I am constantly in search of great books as my best companios for pastime. I found out the list of best books of 20th century on website [goodreads]( https://www.goodreads.com/list/show/6.Best_Books_of_the_20th_Century). Majority of attributes related to the book list can be directly scraped from the web. I used web scrapy to retireve the book list. \n


```{r Trend for century}
renderPlot({
    book_list_decade = book_list %>% select(year, title) %>% 
        mutate(decade=floor((year %/% 10)*10)) %>%
        group_by(decade) %>% summarise(numbers = length(decade))
    ggplot(book_list_decade, aes(x=decade, y=numbers)) + 
        geom_bar(stat = 'identity', fill = 'blue') +
        xlab('Decades of 20th Century') +
        ylab('Number of Books') + 
        ggtitle('Book Distribution Trend for 20th Century') +
        theme(plot.title = element_text(hjust = 0.5, size = 14)) 
})
br()
```

### The trend shows expoential growth decade by decade except year 2000. As 2000 is only one year data, whileas the rest is ten-year data.

Row 
-----------------------------------------------------------------------

```{r Trend by decade}
renderPlot({
    book_list_year_decade = book_list %>% 
        mutate(decade=floor((year %/% 10)*10)) %>% arrange(decade)
    decade_selection = input$decade_choice
    book_list_year_selection = book_list_year_decade %>%
        filter(decade == decade_selection) %>% arrange(year) %>%
        group_by(year) %>% dplyr::summarise(numbers = n())
    ggplot(book_list_year_selection, aes(x=year, y=numbers)) + 
        geom_bar(stat = 'identity', fill = 'blue') +
        xlab(decade_selection) +
        ylab('Number of Books') + 
        ggtitle('Book Distribution Trend per Decade') +
        theme(plot.title = element_text(hjust = 0.5, size = 14)) 
})
```

### The top book distribution per year in each decade is evenly distributed.

Search
=====================================  


### Please select input from sidebar to search books of your interest

```{r Data table for books}
renderDataTable({
    # search book list
      if(!is.null(input$search_item)){
          book_list_matched = return_books(input$search_item, input$search_by)
      } else {
          book_list_matched = book_list
      }
      
    # # order books by the display order
      if(!is.null(input$order_by)){
          book_list_matched = book_list_matched %>% arrange_(.dots=input$order_by)
      }
    
    # presented in datatable
    datatable(book_list_matched,rownames = F)
})
```

Conclusion
=====================================  


###  This project can provide the best book list reommendation in 20th century for interested readers, based on ranking, score, author, title and awards. However, the dataset does not contain the genre category which is important for the readers. The other important missing piece is price. This will be the future improvement. \n

### I shall use selenium to scrape the web so dynamic information can be retrieved, like price.

Row 
-----------------------------------------------------------------------
