---
title: "Best books of 20th Century" 
author: "- M.Sun - Feb. 11, 2018"
# date: "Fubruary 11, 2018"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
#   social: menu
#   source_code: embed
runtime: shiny
---

```{r global}
# load packages
# devtools::install_github('rstudio/rmarkdown')
library(flexdashboard)
library(shinyWidgets)
library(dplyr)
library(DT)
library(ggplot2)
library(magrittr)
library(stringr)

book_list = read.csv('~/NYC_data_science/projects/project2/book_list/book_list.csv', 
                     stringsAsFactors = F)
book_list = book_list %>% select(ranking, year, title, author, pages, 
                                      avg_rating, description, awards) %>%
    filter(year>=1900 & year <2001) 

# global function definition
search_book <- function(pattern_str){
    function(source_str){
        str_detect(source_str, pattern = pattern_str)    
    }
}

# global book search function
# s_pattern: string pattern to be searched
# column_name: list of string sources under column name
# return: a list of books matching the search pattern,
#         ordered by the year and alphabetical order of title
return_books <- function(s_pattern, column_name){
    search_str = search_book(tolower(s_pattern))
    book_column = book_list %>% select(tolower(column_name))
    book_column = sapply(book_column, tolower)
    book_matched = sapply(book_column, search_str)
    book_list_final = book_list %>% filter(book_matched) %>% arrange(year, title)
    return(book_list_final)
}

```

Sidebar {.sidebar}
=====================================
```{r global_sidebar}
radioButtons(inputId = 'decade_choice', 
             label = h3('Select Decade'), 
             choices = list(1900, 1910, 1920, 1930, 1940, 1950, 
                            1960, 1970, 1980, 1990),
             selected = 1990)

searchInput(inputId = 'search_item',
            label = h3('Enter your search:'),
            placeholder = 'This is a placeholder',
            btnSearch = icon('search'),
            btnReset = icon('remove'),
            width = '100%'
)

radioButtons(inputId = 'search_by', 
             label = 'Search Category', 
             choices = list('author', 'title', 'awards'),
             selected = 'author')

checkboxGroupInput(inputId = 'order_by', 
             label = 'Order book list by:', 
             choices = list('ranking', 'year', 'title', 'author','avg_rating'),
             selected = 'ranking')
```

Introduction
=====================================  
###  Great books with great stories always intrigue me. I am constantly in search of great books as my best companios for pastime. There are some apps available to recommend books based on your interests or provide some biased recommendation from expert. I want to find a list that is more neutral. \n

### I found out the list of over 7,000 best books of 20th century on website [goodreads]( https://www.goodreads.com/list/show/6.Best_Books_of_the_20th_Century). The book rankings are based upon the votes by reader. In addition, it also includes the awards list that a specifi book received in the past century. 

Row 
-----------------------------------------------------------------------

Dataset
=====================================  

### Dataset collected includes: 
* #### ranking
* #### year of publishing
* #### book title
* #### author
* #### book pages
* #### book description
* #### average ratings
* #### awards

Row 
-----------------------------------------------------------------------

Trend
=====================================  

### The following two graph shows the top book list in each decade. It is surprising to know the top books were generated in a exponential growth pattern by decade. However, in each decade, the top books were evenly distributed by year.

### The exception is the year 2000, as it is the book list for one year, instead of one decade. 

### The top book distribution per year for each decade can be viewed by choosing the decade in the left panel. \n

<br>

Row 
-----------------------------------------------------------------------


```{r Trend for century}
renderPlot({
    book_list_decade = book_list %>% select(year, title) %>% 
        mutate(decade=floor((year %/% 10)*10)) %>%
        group_by(decade) %>% summarise(numbers = length(decade))
    ggplot(book_list_decade, aes(x=decade, y=numbers)) + 
        geom_bar(stat = 'identity', fill = 'blue') +
        xlab('Decades of 20th Century') +
        ylab('Number of Books') + 
        ggtitle('Book Distribution Trend for 20th Century') +
        theme(plot.title = element_text(hjust = 0.5, size = 14)) 
})
br()
```

Row 
-----------------------------------------------------------------------

```{r Trend by decade}
renderPlot({
    book_list_year_decade = book_list %>% 
        mutate(decade=floor((year %/% 10)*10)) %>% arrange(decade)
    decade_selection = input$decade_choice
    book_list_year_selection = book_list_year_decade %>%
        filter(decade == decade_selection) %>% arrange(year) %>%
        group_by(year) %>% dplyr::summarise(numbers = n())
    ggplot(book_list_year_selection, aes(x=year, y=numbers)) + 
        geom_bar(stat = 'identity', fill = 'blue') +
        xlab(decade_selection) +
        ylab('Number of Books') + 
        ggtitle('Book Distribution Trend per Decade') +
        theme(plot.title = element_text(hjust = 0.5, size = 14)) 
})
```


Row 
-----------------------------------------------------------------------

Search
=====================================  


### Please select input from sidebar to search books of your interest

```{r Data table for books}
renderDataTable({
    # search book list
      if(!is.null(input$search_item)){
          book_list_matched = return_books(input$search_item, input$search_by)
      } else {
          book_list_matched = book_list
      }
      
    # # order books by the display order
      if(!is.null(input$order_by)){
          book_list_matched = book_list_matched %>% arrange_(.dots=input$order_by)
      }
    
    # presented in datatable
    datatable(book_list_matched,rownames = F)
})
```

Conclusion
=====================================  


###  This project can provide the best book list reommendation in 20th century for interested readers, based on ranking, score, author, title and awards. However, the dataset does not contain the genre category which is important for the readers. The other important missing piece is price. This will be the future improvement. \n

Row 
-----------------------------------------------------------------------

Takeaway
===================================== 

### During the web scraping process, I was puzzled by the limitations of web scrapy app. It cannot retrieve dynamic informaiton that was deemed important for this project. After some search and investigation, I found out selesium can be built on top of web scrapy framework. This way, you can take advantage of both the speed of web scrapy and dynamic feature of selenium. I shall use selenium together with web scrapy for the future web scraping project.

Row 
-----------------------------------------------------------------------
